\sysfull

### 2019-07-02 paper/TOSN/systemdescription.tex
Alexei feedback

\paragraph{Programming and Execution Model.}
To use \sys, a programmer must (i) convert a plain C code into tasks by encapsulating the code in a top-level set of functions, (ii) sequence the control-flow between these tasks, and (iii) annotate memory accesses that manipulate task-shared data. Then, they compile and link the code against \sys's runtime, producing a \sys-enabled binary. The runtime relies on \sys's novel {\em adaptive task scheduler} to adapt its execution with the energy conditions. Facilitating efficient task adaptation requires dynamic memory protection which \sys's \emph{virtual memory manager} handles through \emph{page privatization}.

@@

\paragraph{Virtual Memory Manager.}
\sys virtual memory manager (VMM) is the key enabler to ensure memory consistency while coalescing tasks. VMM allows applications to interface with only fast volatile memory pages and privatizes the pages demanded by a coalesced task in order to solve a novel data consistency problem; namely \emph{task coalescing-induced WAR dependency}. VMM achieves page privatization by keeping all page modifications in non-volatile memory on a coalesced task transition. Section~\ref{sec:memory_virtulaization} explains VMM.

>>>>

\paragraph{Programming and Execution Model.}
To use \sys, a programmer must (i) convert a plain C code into tasks by encapsulating the code in a top-level set of functions, (ii) sequence the control-flow between these tasks, and (iii) annotate memory accesses that manipulate task-shared data. Then, they compile and link the code against \sys's runtime, producing a \sys-enabled binary. The runtime relies on \sys's novel {\em adaptive task scheduler} to adapt its execution to the energy conditions. Facilitating efficient task adaptation requires dynamic memory protection which \sys's \emph{virtual memory manager} handles through \emph{page privatization}.

@@

\paragraph{Virtual Memory Manager.}
\sys virtual memory manager (VMM) is the key enabler to ensure memory consistency while coalescing tasks. VMM allows applications to interface with only fast volatile memory pages and privatizes the pages demanded by a coalesced task in order to solve a novel data consistency problem; namely \emph{task coalescing-induced WAR dependencies}. VMM achieves page privatization by keeping all page modifications in non-volatile memory on a coalesced task transition. Section~\ref{sec:memory_virtulaization} explains VMM.
